Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-05-12 code/paper.Rmd
topic model network

@@

@@

ggplot(vandal_edits, 
         aes(n_vandal_edits,
             n_edits,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size =   prop_vandal_edits,
                 colour = prop_vandal_edits)) +
    geom_text_repel(
    data            = vandal_edits %>%  
                      filter(prop_vandal_edits > 0.055),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Proportion of\nedits about vandalism", 
                        labels = c(0, 0.025, 0.05, 0.075),
                        breaks = c(0, 0.025, 0.05, 0.075)) +
  scale_size_continuous(name = "Proportion of\nedits about vandalism", 
                        labels = c(0, 0.025, 0.05, 0.075),
                        breaks = c(0, 0.025, 0.05, 0.075)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits about vandalism",
       y = "Total number of edits") +
    ggtitle("Editing about vandalism on Wikipedia articles")

@@

@@

@@

>>>>

Number of unique editors per page

```{r}
# plot both samples, number of edits per page
bind_rows(revision_history_page_details %>% 
            select(Site, rh_n_editors) %>% 
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl %>% 
            select(Site, rh_n_editors) %>% 
            mutate(Site = "rand")) %>% 
  ggplot(aes(rh_n_editors,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
  scale_fill_viridis_d(labels = c("Random", 
                               "World Heritage")) +
  labs(x = "Number of editors per page",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_editors_per_page.png")
```

Number of unique editors per 1k words per page

```{r}
revision_history_page_details_wordcount <- 
  revision_history_page_details %>% 
  bind_cols(page_data_for_all_pages %>% select(page_wordcount)) %>% 
  mutate(editors_per_1k_words = rh_n_editors / (page_wordcount / 1000))

ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets <- 
bind_cols(ten_k_random_wp_pages, 
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl) %>% 
  mutate(editors_per_1k_words = rh_n_editors / (page_wordcount / 1000))

bind_rows(revision_history_page_details_wordcount %>% 
            select(Site, editors_per_1k_words) %>% 
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets %>% 
            select(Site, editors_per_1k_words) %>% 
            mutate(Site = "rand")) %>% 
  ggplot(aes(editors_per_1k_words,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
  scale_fill_viridis_d(labels = c("Random", 
                               "World Heritage")) +
  labs(x = "Number of editors per 1k words per page",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_editors_density_page.png")
```

@@

ggsave("figures/wh_wikpedia_edits_by_bots.png")
```

@@

ggplot(vandal_edits, 
         aes(n_vandal_edits,
             n_edits,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size =   prop_vandal_edits,
                 colour = prop_vandal_edits)) +
    geom_text_repel(
    data            = vandal_edits %>%  
                      filter(prop_vandal_edits > 0.05),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Proportion of\nedits about vandalism", 
                        labels = c(0, 0.025, 0.05, 0.075),
                        breaks = c(0, 0.025, 0.05, 0.075)) +
  scale_size_continuous(name = "Proportion of\nedits about vandalism", 
                        labels = c(0, 0.025, 0.05, 0.075),
                        breaks = c(0, 0.025, 0.05, 0.075)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits about vandalism",
       y = "Total number of edits") +
    ggtitle("Editing about vandalism on Wikipedia articles")

@@

ggsave("figures/wh_wikpedia_pages_revert_edits.png")

Which articles have the most reverts?

ggplot(revision_history_page_details, 
         aes(rh_user_bot_prop,
             rh_n_edits,
             label = str_wrap(Site, 15))) +
  geom_point(alpha = 0.2,
             aes(size =   rh_revert_prop,
                 colour = rh_revert_prop)) +
    geom_text_repel(
    data            = revision_history_page_details %>%  
                      filter(rh_revert_prop > 0.12),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Proportion of\n edits reverted", 
                        labels = c(0, 0.04, 0.08, 0.12, 0.16),
                        breaks = c(0, 0.04, 0.08, 0.12, 0.16)) +
  scale_size_continuous(name = "Proportion of\n edits reverted", 
                        labels = c(0, 0.04, 0.08, 0.12, 0.16),
                        breaks = c(0, 0.04, 0.08, 0.12, 0.16)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 12) +
  labs(x = "Proportion of bots",
       y = "Total number of edits") +
    ggtitle("Reverted edits on Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_reverts_edits_scatterplot.png")
```

Is there a correlation between reverts and vandalism?

```{r}
left_join(page_data_for_all_pages, vandal_edits) %>% 
  ggplot(aes(rh_revert_prop, 
             prop_vandal_edits,
             size = n_edits)) +
  geom_point() +
  theme_minimal(base_size = 12) +
  labs(x = "Proportion of edits reverted",
       y = "Proportion of edits responding to vandalism") +
    coord_fixed(1)

ggsave("figures/wh_wikpedia_pages_reverts_vandal_edits_scatterplot.png")

@@

tidy_talk <- 
enframe(unlist(wh_wiki_talk_pages)) %>% 
  mutate(clean_text = str_remove_all(value, "\n|\t")) %>% 
  unnest_tokens(word, clean_text) %>% 
  anti_join(stop_words) %>% 
  filter(!word %in% c("article", "page", "talk", "utc", 
                      "class", "edit", "project's",
                      "importance", "rated", "wikiproject",
                      "project", "article", "articles", "article's",
                      "wikipedia", "start", "scale", 
                      "world", "heritage", "sites",
                      "links", "http", "parser", 
                      "output", "mw", "https",
                      "unsigned", "comment")) %>% 
  filter(!str_detect(word, "[[:digit:]]+")) %>% 
  filter(!str_detect(word, ":")) %>% 
  filter(!str_detect(word, "articles")) %>% 
  filter(!str_detect(word, "jump")) %>% 
  filter(!str_detect(word, "\\."))

# top words
tidy_talk %>% 
  count(word, sort = TRUE)

# biggest documents
tidy_talk %>% 
  group_by(name) %>% 
  tally(sort = TRUE)
```

The held-out likelihood is highest between 60 and 80, and the residuals are lowest around 50,

```{r}
library(quanteda)
library(stm)

talk_dfm <- tidy_talk %>%
  count(name, word, sort = TRUE) %>%
  cast_dfm(name, word, n)

# library(slam)
# talk_dfm_stm <- convert(talk_dfm, to = "stm")

# very time consuming
# k_search_output <- 
# searchK(talk_dfm_stm$documents, 
#         talk_dfm_stm$vocab,
#         K = seq(10, 100, 20),
#         cores = 1)
# 
# plot(k_search_output)

# takes a few minutes
topic_model <- stm(talk_dfm, K = 60, 
                   verbose = FALSE, 
                   init.type = "Spectral")

plot(topic_model,  text.cex = 0.75)

td_beta <- tidy(topic_model)

library(drlib) # devtools::install_github("dgrtwo/drlib")

td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    theme_minimal(base_size = 6) +
    labs(x = NULL, y = expression(beta),
         title = "Highest word probabilities for each topic",
         subtitle = "Different words are associated with different topics")

ggsave("figures/wh_wikpedia_pages_talk_page_topics.png")
```

The probability that each document is generated from each topic.

```{r}
td_gamma <- tidy(topic_model, matrix = "gamma",                    
                 document_names = rownames(talk_dfm))

ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 3) +
  labs(title = "Distribution of document probabilities for each topic",
       y = "Number of stories", x = expression(gamma)) +
      theme_minimal(base_size = 6)

@@

we may want to know which topics are associated with each talk page?

```{r}
topic_model_gamma <- tidy(topic_model, matrix = "gamma")

topic_model_gamma %>%
  filter(document %in% 1:10) %>% 
  mutate(title = reorder(document, gamma * topic)) %>%
  ggplot(aes(factor(topic), gamma)) +
  geom_boxplot() +
  facet_wrap(~ title)
```

Topic correlations

```{r}
mod.out.corr <- topicCorr(topic_model)

topic_labels <- labelTopics(topic_model)

topic_tag <- NULL
for(i in 1:nrow(topic_labels$score)){
  topic_tag[[i]] <-  paste0(as_tibble(topic_labels$score)[i, 1:3], collapse = "\n")
}

library(igraph)
g <- graph.adjacency(mod.out.corr$posadj)
V(g)$Degree <- degree(g, mode = 'in') # CALCULATE DEGREE
V(g)$Name <- topic_tag # ADD NAMES
E(g)$weight <- edge.betweenness(g)

library(ggraph)

ggraph(g, layout = "lgl") + 
  geom_edge_link0(aes(width = weight), alpha = 0.1) +
  geom_edge_diagonal(label_colour = "blue", alpha = 0.1) +
    geom_node_point(aes(size = Degree), alpha = 0.6, colour = "steelblue") + 
    geom_node_text(aes(label = Name), size = 3) +
    theme_graph(foreground = 'steelblue', fg_text_colour = 'white')

ggsave("figures/wh_talk_page_topic_correlation_network.png")
```
